---
output: rmarkdown::github_document
editor_options: 
  chunk_output_type: inline
---
```{r pkg-knitr-opts, include=FALSE}
knitr::opts_chunk$set(collapse=TRUE, fig.retina=2, message=FALSE, warning=FALSE)
options(width=120)
```

[![Travis-CI Build Status](https://travis-ci.org/hrbrmstr/delphiepidata.svg?branch=master)](https://travis-ci.org/hrbrmstr/delphiepidata) 
[![Coverage Status](https://codecov.io/gh/hrbrmstr/delphiepidata/branch/master/graph/badge.svg)](https://codecov.io/gh/hrbrmstr/delphiepidata)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/delphiepidata)](https://cran.r-project.org/package=delphiepidata)

# delphiepidata

Query the 'CMU' 'DELPHI' Epidemiological Data 'API'

## Description

The 'CMU' 'DELPHI' (<https://delphi.midas.cs.cmu.edu/>) service provides an aggregated, central point of access to influenza-like illness ('ILI') related data sources. Methods are provided to query all supported endpoints.

- DELPHI API docs: <https://github.com/cmu-delphi/delphi-epidata>
- DELPHI: <https://delphi.midas.cs.cmu.edu/>
- URL: <https://gitlab.com/hrbrmstr/delphiepidata>
- BugReports: <https://gitlab.com/hrbrmstr/delphiepidata/issues>

## What's Inside The Tin

The following functions are implemented:

- `cdc`:	Fetch CDC page hits
- `delphi`:	Fetch Delphi's forecast
- `dengue_nowcast`:	Fetch Delphi's PAHO Dengue nowcast
- `dengue_sensors`:	Fetch Delphi's digital surveillance sensors
- `flusurv`:	Fetch FluSurv data
- `fluview`:	Fetch FluView data
- `fluview_clinical`:	Fetch FluView virological data
- `gft`:	Fetch Google Flu Trends data
- `ght`:	Fetch Google Health Trends data
- `meta`:	Fetch API metadata
- `meta_norostat`:	Fetch NoroSTAT metadata
- `nidss_dengue`:	Fetch NIDSS dengue data
- `nidss_flu`:	Fetch NIDSS flu data
- `norostat`:	Fetch NoroSTAT data (point data, no min/max)
- `nowcast`:	Fetch Delphi's wILI nowcast
- `quidel`:	Fetch Quidel data
- `sensors`:	Fetch Delphi's digital surveillance sensors
- `twitter`:	Fetch HealthTweets data
- `wiki`:	Fetch Wikipedia access data

## Installation

```{r install-ex, eval=FALSE}
devtools::install_git("https://sr.ht.com/~hrbrmstr/delphiepidata.git")
# or
devtools::install_gitlab("hrbrmstr/delphiepidata")
# or (if you must)
devtools::install_github("hrbrmstr/delphiepidata")
```

## Usage

```{r lib-ex}
library(delphiepidata)

# current version
packageVersion("delphiepidata")

```

## delphiepidata Metrics

```{r cloc, echo=FALSE}
cloc::cloc_pkg_md()
```

## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). 
By participating in this project you agree to abide by its terms.
